\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-08 manuscript.Rmd
Figures DPI 1200

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200, fig.width = 6,
 fig.asp = 0.8,out.width = "80%")
#options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Arial")
```

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))

@@

library(jpeg)
export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  writeJPEG("Manuscript.figures/Flowchart1.jpeg",bg = "white", quality = 1)

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg')
```

@@

@@

ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90,colors = c("red", "white", "blue") )
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
```

@@

```{r HullEFA, include=FALSE}
# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(legend.position = "None")

@@

write.csv(full.map, "Table_raw/map_stat")
```
Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=1, 
                  align = "v", 
                  label_size = 12,
                  label_fontfamily = "serif",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 600)
```

@@

knitr::include_graphics('Manuscript.figures/factors.png')

@@

# node definitions with substituted label text
node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
fixedsize = true, fontsize = 35]
F5 [label = 'F5']
F4 [label = 'F4']
F3 [label = 'F3']
F2 [label = 'F2']
F1 [label = 'F1']

node [fontname = Helvetica, shape = box]
b [label = 'item16']
c [label = 'item36']
d [label = 'item17']
e [label = 'item11']
f [label = 'item10']
g [label = 'item12']
h [label = 'item7']
i [label = 'item8']
j [label = 'item9']
k [label = 'item27']
l [label = 'item3']
m [label = 'item40']
n [label = 'item30']
o [label = 'item41']
p [label = 'item33']
q [label = 'item32']
r [label = 'item35']
s [label = 'item37']
t [label = 'item38']
u [label = 'item46']
v [label = 'item45']
w [label = 'item25']
x [label = 'item4']
y [label = 'item1']
z [label = 'item26']

# edge definitions with the node IDs
edge [fontname = Helvetica, fontsize = 35]
F5 -> u [label = '0.60']
F5 -> v [label = '0.59']
F5 -> w [label = '0.41']
F5 -> x [label = '0.41']
F5 -> y [label = '0.40']
F5 -> z [label = '0.35']
F4 -> p [label = '0.74']
F4 -> q [label = '0.73']
F4 -> r [label = '0.66']
F4 -> s [label = '-0.39', color =red]
F4 -> t [label = '0.39']
F3 -> k [label = '0.80']
F3 -> l [label = '0.80']
F3 -> m [label = '0.65']
F3 -> n [label = '0.49']
F3 -> o [label = '36']
F2 -> e [label = '0.79']
F2 -> f[label = '0.76']
F2 -> g [label = '0.65']
F2 -> h[ label = '0.50']
F2 -> i [label = '-.49',color =red]
F2 -> j [label = '0.32']
F1 -> b[label = '0.99']
F1-> c [label = '0.93']
F1-> d [label = '0.80']
}
")

export_svg(EFAplot) %>%
  charToRaw() %>%
  rsvg() %>%
  writeJPEG("Manuscript.figures/EFAplot.jpeg",bg = "white", quality = 1)

@@

residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill=I("grey")) + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+
  labs( y="Frequency")

@@

img1 <- readJPEG("Manuscript.figures/EFAplot.jpeg")

@@

EFAplot.1 <- plot_grid(
 p1, residual.plot,
  labels = "AUTO",
  align="h",
  ncol = 2,
  label_size = 12,
  label_fontfamily = "serif",
  label_fontface = "plain",
  label_y = .98,
  label_x = .04
)

@@

```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE, out.height="80%", out.width="100%", results='asis'}
EFAplot.1

@@

```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives EFA Sample'}
knitr::include_graphics('Manuscript.figures/efagt.png')

@@

```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives of CFA Sample'}
knitr::include_graphics('Manuscript.figures/cfagt.png')

@@

```{r figcfa, fig.cap = "Five Factor CFA Model of LEBA", out.height="150%", out.width="100%",  warning=FALSE}
#library(semPlot)

semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="lisrel",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =6,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          exoCov = FALSE,
          centerLevels = T,
          edge.color="black",
          label.scale=T,
          label.cex=1, #Font of factor and item name
          residuals=FALSE,
           exoVar=FALSE,
          fixedStyle=6, #Style of arrow (guide item)
          freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

F2.itemplots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,
                                   F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 600, bg = "white")

F3.itemplots <- cowplot::plot_grid(F3.iteminfo.1,F3.iteminfo.2, F3.iteminfo.3,
                                   F3.iteminfo.4,F3.iteminfo.5,
                 labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F4.itemplots <- cowplot::plot_grid(F4.iteminfo.1,F4.iteminfo.2, F4.iteminfo.3,
                                   F4.iteminfo.4,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F5.itemplots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2, F5.iteminfo.3,
                                   F5.iteminfo.4,F5.iteminfo.5,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 600, bg = "white")
```

@@

TIC <- cowplot::plot_grid(F1.tic,F2.tic, F3.tic,
                                   F4.tic,F5.tic,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/TIC.png",TIC, width = 10, height = 12, dpi = 600, bg = "white")

@@

knitr::include_graphics('Manuscript.figures/TIC.png')
```

@@

ggsave("Manuscript.figures/personfit.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")

>>>>

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200, fig.width = 6,
 fig.asp = 0.8,out.width = "80%", dev=c('png','postscript'))
#options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Arial")
```

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,tikzDevice)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))

@@

library(jpeg)
export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 1200)

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 800 )
```

@@

```{r}
corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
           ggtheme = ggplot2::theme_minimal(),,tl.srt = 90,colors = c("red", "white", "blue") )+
  theme( panel.grid.major = element_blank(),
         axis.text.x = element_text(size = 8),
         axis.text.y = element_text(size = 8),
         panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
ggsave("Manuscript.figures/corplot.png",corplot, width = 6, height = 6, dpi = 1200, bg ="white")

@@

knitr::include_graphics('Manuscript.figures/corplot.png', dpi =1200)

@@

```{r HullEFA, include=FALSE}
# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ aes(color = "black")+
  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("black", "black"))+theme(legend.position = "None")

@@

write.csv(full.map, "Table_raw/map_stat")
```
Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution. Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution. However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.
```{r factors, include=F}
fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=1, 
                  align = "v", 
                  label_size = 12,
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 1200)
```

@@

knitr::include_graphics('Manuscript.figures/factors.png', dpi =800)

@@

# node definitions with substituted label text
node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
fixedsize = true, fontsize = 40]
F5 [label = 'F5']
F4 [label = 'F4']
F3 [label = 'F3']
F2 [label = 'F2']
F1 [label = 'F1']

node [fontname = Helvetica, shape = box, fontsize = 50, height = 1]
b [label = 'item16']
c [label = 'item36']
d [label = 'item17']
e [label = 'item11']
f [label = 'item10']
g [label = 'item12']
h [label = 'item7']
i [label = 'item8']
j [label = 'item9']
k [label = 'item27']
l [label = 'item3']
m [label = 'item40']
n [label = 'item30']
o [label = 'item41']
p [label = 'item33']
q [label = 'item32']
r [label = 'item35']
s [label = 'item37']
t [label = 'item38']
u [label = 'item46']
v [label = 'item45']
w [label = 'item25']
x [label = 'item4']
y [label = 'item1']
z [label = 'item26']

# edge definitions with the node IDs
edge [fontname = Helvetica, fontsize = 40]
F5 -> u [label = '0.60']
F5 -> v [label = '0.59']
F5 -> w [label = '0.41']
F5 -> x [label = '0.41']
F5 -> y [label = '0.40']
F5 -> z [label = '0.35']
F4 -> p [label = '0.74']
F4 -> q [label = '0.73']
F4 -> r [label = '0.66']
F4 -> s [label = '-0.39', color =red]
F4 -> t [label = '0.39']
F3 -> k [label = '0.80']
F3 -> l [label = '0.80']
F3 -> m [label = '0.65']
F3 -> n [label = '0.49']
F3 -> o [label = '36']
F2 -> e [label = '0.79']
F2 -> f[label = '0.76']
F2 -> g [label = '0.65']
F2 -> h[ label = '0.50']
F2 -> i [label = '-.49',color =red]
F2 -> j [label = '0.32']
F1 -> b[label = '0.99']
F1-> c [label = '0.93']
F1-> d [label = '0.80']
}
")

export_svg(EFAplot) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Manuscript.figures/EFAplot.png",dpi =1200)

@@

residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill=I("grey")) + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12))
  labs( y="Frequency")

@@

img1 <- png::readPNG("Manuscript.figures/EFAplot.png")

@@

EFAplot.1 <- plot_grid(
 p1, residual.plot,
  labels = "AUTO",
  align="h",
  ncol = 2,
  label_size = 12,
  label_fontfamily = "Arial",
  label_fontface = "plain",
  label_y = .99,
  label_x = .04
)

ggsave("Manuscript.figures/EFAfull.png",EFAplot.1, width = 10, height =10, dpi = 1200)

@@

```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}

knitr::include_graphics('Manuscript.figures/EFAfull.png', dpi =1200)
```

@@

```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives EFA Sample'}
knitr::include_graphics('Manuscript.figures/efagt.png',dpi =1200)

@@

```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives of CFA Sample'}
knitr::include_graphics('Manuscript.figures/cfagt.png',dpi =1200)

@@

```{r figcfa, fig.cap = "Five Factor CFA Model of LEBA", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
#library(semPlot)

semPaths (fit.Cor.2 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="lisrel",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =6,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          exoCov = FALSE,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1, #Font of factor and item name
          residuals=FALSE,
           exoVar=FALSE,
          fixedStyle=6, #Style of arrow (guide item)
          freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

F2.itemplots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,
                                   F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")

F3.itemplots <- cowplot::plot_grid(F3.iteminfo.1,F3.iteminfo.2, F3.iteminfo.3,
                                   F3.iteminfo.4,F3.iteminfo.5,
                 labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 1200,bg = "white")

F4.itemplots <- cowplot::plot_grid(F4.iteminfo.1,F4.iteminfo.2, F4.iteminfo.3,
                                   F4.iteminfo.4,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 1200,bg = "white")

F5.itemplots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2, F5.iteminfo.3,
                                   F5.iteminfo.4,F5.iteminfo.5,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")
```

@@

TIC <- cowplot::plot_grid(F1.tic,F2.tic, F3.tic,
                                   F4.tic,F5.tic,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "serif",
                     label_fontface = "plain")
ggsave("Manuscript.figures/TIC.png",TIC, width = 10, height = 12, dpi = 1200, bg = "white")

@@

knitr::include_graphics('Manuscript.figures/TIC.png', dpi =1200)
```

@@

ggsave("Manuscript.figures/personfit.png",personfit , width = 10, height = 12, dpi = 1200, bg = "white")
